---
title: "WICKED WINES"
subtitle: Wine Buying Behaviour of US Consumers
date: "23 Oct 2020 (updated on `r Sys.Date()`)"
output:
  bookdown::pdf_document2:
    toc: true
    toc_float: 
      collapsed: false
toccolor: blue
urlcolor: blue
linkcolor: blue
---

\newpage

<!-- globle code chunk options -->

```{r global-chunk-options, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      warning = F,
                      message = F,
                      fig.retina = 3
                    #  dev = "svg"
                    )
```

<!-- all r packages used in this analysis -->

```{r packages-used, include=FALSE}
library(lubridate) # for now function
library(tidyverse)
library(skimr)
library(visdat) # viz missing data
library(sjPlot)
library(hablar)
library(tinytex)
```

# Data1: Consumer feelings toward wine

```{r import-data, include=FALSE}
## Import data
library(readxl)
wcons <- read_excel("data/Research_SPSS.xlsx")

#tibble::glimpse(wcons)
```

<!-- ## Variables renamed -->

```{r rename, include=FALSE}
wcons <- wcons %>% 
  rename(id = "Participant ID",
         age = "Age",
    adequate = "1",
         irrelevant = "2",
         interest = "3",
         decision = "4",
         care = "5",
         choose = "6",
         discount = "7",
         think = "8",
         status = "9",
         read = "10",
         color = "11",
         aroma = "12",
         course = "13",
         positive = "14",
         fairs = "15",
         enjoy = "16",
         image = "17",
         indulge = "18",
         benefit = "19",
         type = "20",
         easy = "21",
         learn = "22",
    pubspec = "23-Wine Spectator",
    pubenth = "23-Wine Enthusiast",
    pubadv = "23-Robert Parker's Wine Advocate",
    pubfoo = "23-Food & Wine",
    pubapp = "23-Bon Appetit",
    pubdec = "23-Decantur",
    sublist = "24",
    ptrcd = "25-a",
    pt90 = "25-b",
    ptabs = "25-c",
    ptatt = "25-d",
    ptunf = "25-e",
    chopt = "26-a",
    chont = "26-b",
    chofrds = "26-c",
    chostrs = "26-d",
    chorvw = "26-e",
    chopub = "26-f",
    choweb = "26-g",
    chopro = "26-h",
    wedu = "27",
    crstas = "28-a",
    crsuni = "28-b",
    crsdin = "28-c",
    crsweb = "28-d",
    crssem = "28-e",
    crsself = "28-f",
    chonot = "29-a",
    chopri = "29-b",
    chopnt = "29-c",
    choadv = "29-d",
    chofrd = "29-e",
    choind = "29-f",
    chostr = "29-g",
    chooth = "29-h",
    consout = "30",        
    spendout = "31",
    conshm = "32",
    spendhm = "33",
    gender = "34",
    marital = "35",
    edu = "36",
    ethnic = "37",
    income = "38"
    ) 

names(wcons)
```

## Missing values

```{r plot-missing, fig.cap="Pattern of missing values"}
visdat::vis_miss(wcons)
```

\newpage

## Consumer feelings toward wine

```{r wfeel-var}
wfeel <- wcons %>% 
  select(3:24)

#names(wfeel)

x <- wfeel %>% 
  mutate(wfeel_score = adequate + irrelevant + interest +
           decision + care + choose + discount + think + status + read + color + aroma + course + positive + fairs + 
           enjoy + image + indulge + benefit + type + easy + learn) 


```

```{r plot-wfeel, fig.height=6.7, fig.cap="Consumer feelings toward wine and wine consumption"}
set_theme(
  legend.pos = "bottom",
  base = theme_bw()
          )

sjPlot::plot_likert(
  wfeel,
  grid.range = c(1.8, 1),
  expand.grid = F,
  values = "sum.outside",
  show.prc.sign = TRUE,
  geom.colors = "RdPu",
  legend.pos = c("bottom"),
  #title = "Consumer feelings toward wine and wine consumption",
  legend.labels = c(" 1 Definitely not me", "2", "3 Neutral", "4", "5 Totally me"),
  cat.neutral = 3,
  reverse.scale = TRUE,
  group.legend.options = list(nrow = 2),
  show.n = F,
  ) 
  
```

\newpage

# Influence of brand on wine enjoyment

## Round 1

```{r types-round1, include=FALSE}
round1 <- read_csv("data/round1.csv")

names(round1)

round1a <- round1 %>% 
  select(participant1, brand1, enjoy1, drink1)

names(round1a)

round1a$enjoy1 <- as.factor(round1a$enjoy1)

round1a$brand1 <- as.factor(round1a$brand1)

round1a$drink1 <- as.factor(round1a$drink1)

glimpse(round1a)
```

```{r plot-round1}
ggplot2::ggplot(
  data = round1a,
  mapping = aes(fill = brand1,
                y = enjoy1)
                ) +
  geom_bar(
    position = position_fill(reverse = TRUE) # percent stacked & to keep the colour order of bars & legend same
  ) +
  scale_fill_manual(
    values = c("maroon4", "pink", "maroon2", "pink", "maroon2"), 
    labels=c("Scarecrow", "Hook or Crook", "Materium", "Precision", "Kapscandy")) +
  labs(
    title = "ROUND1 1",
    subtitle = "Level of wine enjoyment as per the brand",
       caption = "",
       x = "Percentage of participants",
       y = "Level of enjoyment",
    fill = "Wine Brands:"
    ) +
  guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
  scale_y_discrete(
    labels=c("1" = "Lowest Enjoyed 1", "5" = "Highest Enjoyed 5")) 
```

## Round 2

```{r types-round2, include=FALSE}
round2 <- read_csv("data/round2.csv")

names(round2)

round2a <- round2 %>% 
  select(participant2, brand2, enjoy2, drink2)

names(round1a)

round2a$enjoy2 <- as.factor(round2a$enjoy2)

round2a$brand2 <- as.factor(round2a$brand2)

round2a$drink2 <- as.factor(round2a$drink2)

glimpse(round2a)
```

```{r plot-round2}
ggplot2::ggplot(
  data = round2a,
  mapping = aes(fill = brand2,
                y = enjoy2)
                ) +
  geom_bar(
    position = position_fill(reverse = TRUE) # percent stacked & to keep the colour order of bars & legend same
  ) +
  scale_fill_manual(
    values = c("maroon4", "pink", "maroon2", "pink", "maroon2"), 
    labels=c("Scarecrow", "Hook or Crook", "Materium", "Precision", "Kapscandy")) +
  labs(
    title = "ROUND 2",
    subtitle = "Level of wine enjoyment as per the brand",
       caption = "",
       x = "Percentage of participants",
       y = "Level of enjoyment",
    fill = "Wine Brands:"
    ) +
  guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
  scale_y_discrete(
    labels=c("1" = "Lowest Enjoyed 1", "5" = "Highest Enjoyed 5")) 
```

## Round 3

```{r types-round3, include=FALSE}
round3 <- read_csv("data/round3.csv")

names(round3)

round3a <- round3 %>% 
  select(participant3, brand3, enjoy3, drink3)

names(round3a)

round3a$enjoy3 <- as.factor(round3a$enjoy3)

round3a$brand3 <- as.factor(round3a$brand3)

round3a$drink3 <- as.factor(round3a$drink3)

glimpse(round3a)
```

```{r plot-round13}
ggplot2::ggplot(
  data = round3a,
  mapping = aes(fill = brand3,
                y = enjoy3)
                ) +
  geom_bar(
    position = position_fill(reverse = TRUE) # percent stacked & to keep the colour order of bars & legend same
  ) +
  scale_fill_manual(
    values = c("maroon4", "pink", "maroon2", "pink", "maroon2"), 
    labels=c("Scarecrow", "Hook or Crook", "Materium", "Precision", "Kapscandy")) +
  labs(
    title = "ROUND 3",
    subtitle = "Level of wine enjoyment as per the brand",
       caption = "",
       x = "Percentage of participants",
       y = "Level of enjoyment",
    fill = "Wine Brands:"
    ) +
  guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
  scale_y_discrete(
    labels=c("1" = "Lowest Enjoyed 1", "5" = "Highest Enjoyed 5")) 
```

\newpage

# Desired wine feature

This will help us to understand for which brand which particular attribute is playing a major role in the higher or lower wine enjoyment score.

```{r round1-data-long, include=FALSE}
# roud 1 data
names(round1)

glimpse(round1)

# variable dbl to factors
round1$participant1 <- as.factor(round1$participant1)

round1$enjoy1 <- as.factor(round1$enjoy1)

round1$brand1 <- as.factor(round1$brand1)

round1$drink1 <- as.factor(round1$drink1)

glimpse(round1)

# from wide to long data

round1_long <- gather(
  round1,
  feature1,
  cond1,
  "Tannin:Low":"Alcohol Level:High",
  factor_key = TRUE
)

round1_long$cond1 <- as.factor(round1_long$cond1)

# long data
glimpse(round1_long)

table(round1_long$feature1, round1_long$cond1)
```

```{r round2-data-long, include=FALSE}
# roud 2 data
names(round2)

glimpse(round2)

# variable dbl to factors
round2$participant2 <- as.factor(round2$participant2)

round2$enjoy2 <- as.factor(round2$enjoy2)

round2$brand2 <- as.factor(round2$brand2)

round2$drink2 <- as.factor(round2$drink2)

glimpse(round2)

# from wide to long data

round2_long <- gather(
  round2,
  feature2,
  cond2,
  "Tannin:Low":"Alcohol Level:High",
  factor_key = TRUE
)

round2_long$cond2 <- as.factor(round2_long$cond2)

# long data
glimpse(round2_long)

table(round2_long$feature2, round2_long$cond2)
```

```{r round3-data-long, include=FALSE}
# roud 1 data
names(round3)

glimpse(round3)

# variable dbl to factors
round3$participant3 <- as.factor(round3$participant3)

round1$enjoy3 <- as.factor(round3$enjoy3)

round3$brand3 <- as.factor(round3$brand3)

round3$drink3 <- as.factor(round3$drink3)

glimpse(round3)

# from wide to long data

round3_long <- gather(
  round3,
  feature3,
  cond3,
  "Tannin:Low":"Alcohol Level:High",
  factor_key = TRUE
)

round3_long$cond3 <- as.factor(round3_long$cond3)

# long data
glimpse(round3_long)

table(round3_long$feature3, round3_long$cond3)
```

```{r plot-round2-long}
round1_long %>% 
  
  ggplot2::ggplot(aes(
    y = feature1,
    fill = cond1
  )) +
  geom_bar() +
  guides(fill = guide_legend(reverse=TRUE)) +
  scale_fill_manual(
    values = c("pink", "maroon4"), 
    labels=c("Not Desired", "Desired")) + 
  labs(
    title = "ROUND 1",
    subtitle = "",
       caption = "",
       x = "Frequency",
       y = "Wine Attributes",
    fill = "Features:"
    ) +
  theme_bw() +
  theme(legend.position = "bottom")
```

```{r plot-round1-long}
round2_long %>% 
  ggplot2::ggplot(aes(
    y = feature2,
    fill = cond2
  )) +
  geom_bar() +
  guides(fill = guide_legend(reverse=TRUE)) +
  scale_fill_manual(
    values = c("pink", "maroon4"), 
    labels=c("Not Desired", "Desired")) + 
  labs(
    title = "ROUND 2",
    subtitle = "",
       caption = "",
       x = "Frequency",
       y = "Wine Attributes",
    fill = "Features:"
    ) +
  theme_bw() +
  theme(legend.position = "bottom")
```

```{r plot-round3-long}
round3_long %>% 
  ggplot2::ggplot(aes(
    y = feature3,
    fill = cond3
  )) +
  geom_bar() +
  guides(fill = guide_legend(reverse=TRUE)) +
  scale_fill_manual(
    values = c("pink", "maroon4"), 
    labels=c("Not Desired", "Desired")) + 
  labs(
    title = "ROUND 3",
    subtitle = "",
       caption = "",
       x = "Frequency",
       y = "Wine Attributes",
    fill = "Features:"
    ) +
  theme_bw() +
  theme(legend.position = "bottom")
```

# Chi square tests

## Brand and Enjoyment

### Round 1

```{r chi-test-round1}
# uncomment it to see table
#table(round1a$brand1, round1a$enjoy1)

test4 <- chisq.test(table(round1a$brand1, round1a$enjoy1))

test4
```

### Round 2

```{r chi-test-round2}
# uncomment it to see table
# table(round2a$brand2, round2a$enjoy2)

test5 <- chisq.test(table(round2a$brand2, round2a$enjoy2))

test5
```

### Round 3

```{r chi-test-round3}
# uncomment it to see table
#table(round3a$brand3, round3a$enjoy3)

test6 <- chisq.test(table(round3a$brand3, round3a$enjoy3))

test6
```

In three different studies how consumer's level of wine enjoyment related with their intention to re-drink the same wine?

Pearson's **chi-square test** is used to find the correlation between the level of wine enjoyment and consumer's intention to re-drink the same wine.

## Enjoy and Re-drink

### Round 1

```{r}
#round1a %>% 
#  names()

#table(round1a$enjoy1)

#table(round1a$drink1)

#table(round1a$enjoy1, round1a$drink1)

test1 <- chisq.test(table(round1a$enjoy1, round1a$drink1))

test1
```

### Round 2

```{r}
#round2a %>% 
#  names()

#table(round2a$enjoy2)

#table(round2a$drink2)

#table(round2a$enjoy2, round2a$drink2)

test2 <- chisq.test(table(round2a$enjoy2, round2a$drink2))

test2
```

### Round 3

```{r}
#round3a %>% 
#  names()

#table(round3a$enjoy3)

#table(round3a$drink2)

#table(round3a$enjoy3, round3a$drink3)

test3 <- chisq.test(table(round3a$enjoy3, round3a$drink3))

test3
```
